State of The Practice in Indirect Conflicts: Causes, Mitigation Strategies, and Future Directions

### 2014-03-16 iced-2013/paper.tex
ICED done.

Many indirect conflict tools have been developed, tested, and published. Sarma et al.~\cite{Sarma:2007:TSA} created Palantir,
which can both detect potential indirect conflicts, at the class signature level, and alert developers to these conflicts.
Palantir represented one of the first serious attempts at aiding developers towards indirect conflicts. Holmes et
al.~\cite{Holmes:2010:CAR} take it one step further with their tool YooHoo, by detecting fine grained source code changes,
such as method return type changes, and create a taxonomy for different types of changes and their proneness to cause
indirect conflicts. This tool and its taxonomy had a severely reduced false positive rate, however, the true positives
detected may already be detectable by current tools such as compilers and unit testing. The tool Ariadne~\cite{Trainer:2005:BGT}
creates an environment where developers can see how source code changes will affect other areas of a project at the
method level, using method call graphs, showing where indirect conflicts may occur. This type of exploratory design has
been used often in the visualization of indirect conflict tools, allowing developers a type of search area for their development
needs. Another indirect conflict tool, CASI~\cite{Servant:2010:CPI}, utilizes dependency slicing~\cite{Bajracharya:2009:SIS}
instead of method call graphs to provide an environment to see what areas of a project are being affected by a source code change.
The evaluations of these tools indicate that they have the same common difficulties of scalability, false positives, and information overload. Our own tool
Impact!~\cite{Ell:2013} also suffered these same fates.

Since Cataldo et al.~\cite{Cataldo:2006:ICR} have shown that socio-technical congruence can be leveraged to improve task completion
times, many indirect conflict tools support the idea of a socio-technical congruence~\cite{Kwan:2011:ESC} in order to help
developers solve their indirect conflict issues through social means~\cite{Begel:2010:CDE}~\cite{Borici:2012:CHA}.
Begel et al.~\cite{Begel:2010:CDE} created Codebook, a type of social developer network related directly to source code
artifacts, which can be used to identify developers and expert knowledge of the code base. Borici et al.~\cite{Borici:2012:CHA}
created ProxiScientia which used technical dependencies between developers to create a network of coordination needs.
However, again the problems of scalability and information overload become a factor.

@@

Questionnaire participants were invited to participate in the questionnaire by email. We directly emailed 1300 participants and obtained 78 responses
giving a response rate of 6\%. We attribute the low response rate with: the questionnaires
were conducted during the months of July and August while many participants may be away from their regular positions.

The questionnaire we designed ~\footnote{http://thesegalgroup.org/projects/indirect-conflicts/}
was based on the insights we obtained from the round of interviews, and was intended to confirm these insights but also to broaden them to a larger sample size of developers who may have similar or different opinions from those already acquired from the interviews. The question topics asked in the questionnaire were:

@@

The direct implication this research has on tool development is that of current adoption among developers. As was stated,
developers are more keen to invest their time at the detection and cure / resolution stages of indirect conflicts. That being
said, focus at these two stages for tool developer will lead to larger adoption among developers.
It should be noted here that detection must come with an almost zero rate of false positives as
current tools (unit and integration and user testing), while they may not have 100\% recall, have almost 100\% precision.

>>>>

Many indirect conflict tools have been developed, tested, and published. Sarma et al.~\cite{Sarma:2007:TSA} created Palantir,
which can both detect potential indirect conflicts, at the class signature level, and alert developers to these conflicts.
Palantir represented one of the first serious attempts at aiding developers towards indirect conflicts. Holmes et
al.~\cite{Holmes:2010:CAR} take it one step further with their tool YooHoo, by detecting fine grained source code changes,
such as method return type changes, and create a taxonomy for different types of changes and their proneness to cause
indirect conflicts. This tool and its taxonomy had a severely reduced false positive rate, however, the true positives
detected may already be detectable by current tools such as compilers and unit testing. The tool Ariadne~\cite{Trainer:2005:BGT}
creates an environment where developers can see how source code changes will affect other areas of a project at the
method level, using method call graphs, showing where indirect conflicts may occur. This type of exploratory design has
been used often in the visualization of indirect conflict tools, allowing developers a type of search area for their development
needs. Another indirect conflict tool, CASI~\cite{Servant:2010:CPI}, utilizes dependency slicing~\cite{Bajracharya:2009:SIS}
instead of method call graphs to provide an environment to see what areas of a project are being affected by a source code change.
The evaluations of these tools (including our own prototype Impact! ~\cite{Ell:2013}) indicate that they have the same common difficulties of scalability, false positives, and information overload.

Following Cataldo et al.~\cite{Cataldo:2006:ICR}'s work that indicated that socio-technical congruence can be leveraged to improve task completion
times, many indirect conflict tools support the idea of a socio-technical congruence~\cite{Kwan:2011:ESC} in order to help
developers solve their indirect conflict issues through social means~\cite{Begel:2010:CDE}~\cite{Borici:2012:CHA}.
Begel et al.~\cite{Begel:2010:CDE} created Codebook, a type of social developer network related directly to source code
artifacts, which can be used to identify developers and expert knowledge of the code base. Borici et al.~\cite{Borici:2012:CHA}
created ProxiScientia which used technical dependencies between developers to create a network of coordination needs.
However, again the problems of scalability and information overload become a factor.

@@

Questionnaire participants were invited to participate in the questionnaire by email. We directly emailed 1300 participants and obtained 78 responses
giving a response rate of 6\%. We attribute the low response rate with the questionnaires
being sent out during the months of July and August when many participants may be away from their regular positions.

We designed the questionnaire~\footnote{http://thesegalgroup.org/projects/indirect-conflicts/} to follow the interviews. We intended to confirm some of the insights we obtained from the interviews with a larger sample size of developers who may have similar or different opinions from those already acquired from the interviews. The question topics asked in the questionnaire were:

@@

The direct implication this research has on tool development is that of current adoption among developers. As was stated,
developers are more keen to invest their time at the detection and cure / resolution stages of indirect conflicts. We believe that focus at these two stages for tool developer will lead to larger adoption among developers.
Similarly, detection must come with an almost zero rate of false positives as current tools (such as unit and integration tests) only report real problems with almost 100\% precision (even though their recall may not be 100\%).

%It should be noted here that detection must come with an almost zero rate of false positives as
%current tools (unit and integration and user testing), while they may not have 100\% recall, have almost 100\% precision.
